\thesistitle

### 2019-08-02 sections/abstract.tex
Changes to overall structure
Better table (now it fits :diamond_shape_with_a_dot_inside:)
Ana

\chapter*{Abstract}
\todo[inline,color=blue!10]{This should be done when most of the rest of the document is finished. Be concise, introduce context, problem, known approaches, your solution, your findings.}

Duplication in source code can have a major negative impact on the maintainability of source code. There are several techniques that can be used in order to merge clones, reduce duplication, improve the design of the code and potentially also reduce the total volume of a software system. In this study, we look into the opportunities to aid in the process of refactoring these duplication problems for object-oriented programming languages.

>>>>

\chapter*{Abstract}
%\todo[inline,color=blue!10]{This should be done when most of the rest of the document is finished. Be concise, introduce context, problem, known approaches, your solution, your findings.}
\todo{Update the abstract}
Duplication in source code can have a major negative impact on the maintainability of source code. There are several techniques that can be used in order to merge clones, reduce duplication, improve the design of the code and potentially also reduce the total volume of a software system. In this study, we look into the opportunities to aid in the process of refactoring these duplication problems for object-oriented programming languages. We focus primarily on the Java programming language, as refactoring in general is very language-specific.

### 2019-08-02 sections/background.tex
Variable refactoring
Ana

public void doAandB(){
  doA();
  doB();
}
\end{javacode}}
\end{parcolumns}
\caption{Refactoring duplication through method extraction.}
\label{fig:extractmethod}
\end{figure}

@@

Regarding refactoring, a software system can often not change the source code of its dependencies. This can sometimes be a burden, when an external dependency does not use proper abstractions that are required by a software system. Because of that, in this study, we differentiate between internal and external classes to see what impact they have on the refactoring process.

@@

\section{Git}
\todo{TODO}

>>>>

public void doAandB(){
  doA();
  doB();
}
\end{javacode}}
\end{parcolumns}
\caption{Refactoring a clone class through method extraction.}
\label{fig:extractmethod}
\end{figure}

@@

Regarding refactoring, a software system can often not change the source code of its dependencies. This can sometimes be a burden, when an external dependency does not use proper abstractions that are required by a software system. Because of that, in this study, we differentiate between internal and external classes to see what impact they have on the refactoring process.\todo{you don't consider external right?}

@@

### 2019-08-02 sections/introduction.tex
Ana

The process of improving maintainability through the refactoring of duplicate code is time consuming and error-prone. This process mainly consists of these two aspects:
\begin{itemize}
	\item Find refactoring candidates, either tool-assisted or manually.
	\item Refactor identified candidates, either tool-assisted or manually.
\end{itemize}
There are tools that assist in the process of finding duplicate code, but none of these tools identify all duplication problems. Often, these clone detection tools result in false-positives and false-negatives \cite{roy2007survey}. We define false-negatives as clones that can and should be refactored but are not found due to the configuration by which they are detected. We define false-positives as clones that do not improve the system maintainability when refactored. Many false-negatives are due to the thresholds that are used. Many clone detection tools \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval} only consider clones that have a minimum of 6 lines. Using such an approach is bound to result in many false-negatives, but using a lower threshold is shown to increase the number of false-positives. %TODO cite threshold paper

>>>>

The process of improving maintainability through the refactoring of duplicate code is time consuming and error-prone. This process mainly consists of these two aspects:
\begin{itemize}
	\item Find refactoring candidates, either tool-assisted or manually.
	\item Refactor identified candidates, either tool-assisted or manually.
\end{itemize}
There are tools that assist in the process of finding duplicate code, but none of these tools identify all duplication problems. Often, these clone detection tools result in false-positives and false negatives \cite{roy2007survey}. We define false negatives as clones that can and should be refactored but are not found due to the configuration by which they are detected. We define false-positives as clones that do not improve the system maintainability when refactored. Many false negatives are due to the thresholds that are used. Many clone detection tools \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval} only consider clones that have a minimum of 6 lines. Using such an approach is bound to result in many false negatives, but using a lower threshold is shown to increase the number of false-positives. %TODO cite threshold paper
